%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Technology Summer Analyst} % Job title
    {Accenture} % Organisation
    {Toronto, ON} % Location
    {June 2025 - Aug 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Reduced Azure cloud costs by restructuring Azure Monitor logs, optimizing SQL databases, rightsizing VMs, and leveraging Azure Monitor recommendations.}
        \item {Built Power BI dashboards integrated with Azure Cost Management + Billing with automated refresh, MTD filtering, and cost breakdowns by component.}
        \item {Developed PowerShell scripts to audit multi-tenant environments for aged Azure resources (e.g., unmanaged disks and snapshots), exporting to structured CSVs.}
        \item {Implemented Logic Apps workflow to autoscale Microsoft Fabric capacity on a schedule, reducing off-hours resource spend.}
      \end{cvitems}
    }
    
  \cventry
    {Network Operations} % Job title
    {Halton District School Board} % Organisation
    {Burlington, ON} % Location
    {May 2023 - Sept 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Installed and configured network hardware, including switches and access points, across schools in the Halton region.}
        \item {Diagnosed and resolved network and system issues on board devices such as laptops and desktops.}
        \item {Independently developed detailed switch topology and documentation to optimize school network infrastructure.}
        \item{Improved network performance and reliability across over 100 schools, ensuring seamless connectivity for students and staff.}
      \end{cvitems}
    }

\end{cventries}
