%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Personal Project} % Organisation
    {Budget Tool} % Project
    {February 2026} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Built a self-hosted budgeting app with Next.js, TypeScript, Tailwind CSS, and SQLite w/ authenticated accounts and server-side cookie sessions.}
        \item {Designed multi-plan budgeting workflows (create, switch, rename, delete) with autosaved state and monthly cash-flow projections.}
        \item {Hardened API security using origin/host checks, restrictive security headers, and rate limiting for auth and general endpoints.}
        \item {Containerized deployment using Docker.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Personal Project} % Organisation
    {Sweetside Band Website} % Project
    {January 2026} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Built a website for a local band using Next.js, React, TypeScript, and Tailwind CSS with responsive layouts and reusable UI components.}
        \item {Used a JSON-driven content system for band details, shows, members, and media, enabling non-technical updates without code changes.}
        \item {Containerized deployment using Docker.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Software System Development \& Integration} % Organisation
    {vCard Management System} % Project
    {Winter 2025} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a C library to parse and validate vCard files according to RFC 6350, handling custom error codes, parameters, and edge cases.}
        \item {Built a Python GUI to display, modify, and export vCard data, integrating with a SQLite database for persistent contact storage.}
        \item {Implemented end-to-end data flow from file parsing to UI and database operations, ensuring robust memory and error handling.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
